\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2014-09-04 doc/acknowledgments.tex
AV acknowledgement

We are also grateful to Brooke Simmons, David Hogg, XXX and YYY for many useful
conversations about citizen science and gravitational lens detection. % Need to
cross-ref with Zooniverse author list
%
PJM was given support by the Royal  Society, in the form of a research
fellowship, and by the U.S. Department of Energy under contract number DE-AC02-76SF00515.
% He would like to thank the DotAstronomy community for
% introducing so many valuable concepts and tools, and David Harris and
% Roger Davies for valuable conversations about community-building.
%
% AV \ldots
%
% AM \ldots
The work of AM and SM was supported by World Premier International Research
Center Initiative (WPI Initiative), MEXT, Japan.
%
% Zooniverse / Sloan Foundation.
%
The \sw project is open source, and was developed at
https://github.com/drphilmarshall/SpaceWarps.

>>>>

We are also grateful to Brooke Simmons, David Hogg, XXX and YYY for many useful
conversations about citizen science and gravitational lens detection. 
%
PJM was given support by the Royal Society, in the form of a research
fellowship, and by the U.S. Department of Energy under contract number DE-AC02-76SF00515.
%
AV acknowledges support from the Leverhulme Trust in the form of a research
fellowship.
%
The work of AM and SM was supported by World Premier International Research
Center Initiative (WPI Initiative), MEXT, Japan.
%
% Zooniverse / Sloan Foundation.
% 
% Other authors.
%
The \sw project is open source. 
The web app was developed at https://github.com/Zooniverse/Lens-Zoo
while the SWAP analysis software was developed at
https://github.com/drphilmarshall/SpaceWarps.
